### 2015-12-11 paper/3-features.tex
Proofread introduction to section 3

Historically, dxex is based on PythonPDEVS~\cite{PythonPDEVS}.
While Python is a good language to create software prototypes, its performance has proven to be insufficient to compete with other simulation kernels~\cite{MasterThesis}.
Dxex implements only a subset of PythonPDEVS, but makes some of its own additions.
The core simulation algorithm and optimizations, however, are highly similar.

While we will not make a detailed comparison with PythonPDEVS here, but will attempt to provide a brief overview of some supported features.
Similarly to PythonPDEVS, dxex supports direct connection~\cite{SymbolicFlattening}, \textsf{Dynamic Structure DEVS}~\cite{DSDEVS}, termination conditions, and a modular tracing and scheduling framework~\cite{PythonPDEVS}.
But whereas PythonPDEVS only supports optimistic synchronization, dxex support multiple synchronization protocols.
This is in line with the design principles of PythonPDEVS: offer users the option to pass information on how to efficiently simulate the model.
In our case, it now becomes possible to pass the simulation kernel the ``hint'' as to which synchronization protocol would be ideal for this model.
Furthermore, the implementation in C++11 allows many more (static) optimizations, which were plainly impossible when using an interpreted language.

Note that, since there is no universal \textsf{DEVS} model standard, dxex models are incompatible with PythonPDEVS and vice versa.
This is due to dxex models being grafted on C++11, whereas PythonPDEVS models are grafted on Python.

In the remainder of this section, we will elaborate on our prominent new feature: support for multiple synchronization protocols within the same simulation tool.

>>>>

Historically, dxex is based on PythonPDEVS~\cite{PythonPDEVS}.
Python is a good language for prototypes, but performance has proven insufficient to compete with other simulation kernels~\cite{MasterThesis}.
Dxex is a C++11-based implementation of PythonPDEVS, but implements only a subset of PythonPDEVS, whiel making some of its own additions.
So while the feature set is not too comparable, the architectural design, core simulation algorithm, and optimizations, are highly similar.

We will not make a detailed comparison with PythonPDEVS here, but only mention some supported features.
Dxex supports, similarly to PythonPDEVS, the following features: direct connection~\cite{SymbolicFlattening}, \textsf{Dynamic Structure DEVS}~\cite{DSDEVS}, termination conditions, and a modular tracing and scheduling framework~\cite{PythonPDEVS}.
But whereas PythonPDEVS only supports optimistic synchronization, dxex support multiple synchronization protocols.
This is in line with the design principle of PythonPDEVS: allow users to pass performance hints to the simulation kernel.
In our case, a user can pass the simulation kernel the ``hint'' as to which synchronization protocol must be used for this model.
Our implementation in C++11 also allows for optimizations which were plainly impossible in an interpreted language.

Since there is no universal \textsf{DEVS} model standard, dxex models are incompatible with PythonPDEVS and vice versa.
This is due to dxex models being grafted on C++11, whereas PythonPDEVS models are grafted on Python.

In the remainder of this section, we will elaborate on our prominent new feature: support for multiple synchronization protocols within the same simulation tool, which are offered transparantly to the model.
